Morse Theory

### 2020-12-03 paper.tex

The new method uses Reeb graphs to simplify triangulation. This allows us to save the topological properties of the model after simplification. The idea of the algorithm is to remove those vertices whose geodesic distance to the vertices of the Reeb graph of the model is the smallest. This way we get a more accurate triangulation, with fewer edges. Thanks to the use of the Reeb graphs, all topological properties are preserved in the construction fig. \ref{fig:New_alg}.
\begin{figure}[h!]
\center{\includegraphics[scale=0.3]{New_alg.png}}
\caption{Comparison of QEM method and the mew algorithm using Reeb graphs}
\label{fig:New_alg}
\end{figure}

>>>>

The new method uses Reeb graphs to simplify triangulation. This allows us to save the topological properties of the model after simplification. The idea of the algorithm is to remove those vertices whose geodesic distance to the vertices of the Reeb graph of the model is the smallest. This way we get a more accurate triangulation, with fewer edges. Thanks to the use of the Reeb graphs, all topological properties are preserved in the construction fig. \ref{fig:New_alg}.
\begin{figure}[h!]
\center{\includegraphics[scale=0.3]{New_alg.png}}
\caption{Comparison of QEM method and the mew algorithm using Reeb graphs}
\label{fig:New_alg}
\end{figure}
\subsection{Oceanography}
    Reeb graphs are used in Oceanography to analyze the flows in the deep ocean. The neutral density $\gamma^n$ is a density variable that is used 
    for describing the so called neutral density surfaces which are aligned with the neutral tangent plane. The flows in the deep ocean are believed to be aligned with the neutral
    tangent plane.

    A neutral surface is a surface that is everywhere parallel to the neutral tangent plane. It is proved that this plane and all neutral surfaces are normal to
    the dianeutral vector:
   $$
    \vec{N}=\rho(\beta \nabla S-\alpha \nabla\theta)
   $$

   where $S$ is the salinity, $\theta$ is the potential temperature, $\alpha$ is the thermal expansion coefficient,
   and $\beta$ is the saline concentration coefficient. Therefore, neutral surfaces are perpendicular to $\vec{N}$ in every point. It is proved that:

   The neutral density is a function of latitude and longitude. The spatial dependence is fundamental property
   of neutral surfaces. Since the gradients of $S$ and $\theta$ within a neutral surface are aligned, their contours are also aligned.
   Therefore, there is a functional relationship between these variables. It is proved that the regions where
   the function is single-valued are the regions associated with the edges of the Reeb graph of $\theta$ on the surface.
